{
\itshape
\begin{center}
    "Gratitude is the only treasure of the humble."
\end{center}
\begin{flushright}
William Shakspeare
\end{flushright}
I would like to begin by thanking my thesis advisor, Professor Davit Harutyunyan, for his exceptional guidance and scientific insight. His contribution to my development was immense, not just through his guidance but also by allowing me the independence to conduct my own research. I am also deeply grateful to all the professors at UCSB from whom I have had the privilege to learn. Their dedication and the excellence within this department have greatly enriched my experience.

I must also acknowledge all the friends I have made during my PhD journey. Being surrounded by such a brilliant group of individuals not only broadened our perspectives but also filled our collective experience with memorable and fun moments.

My heartfelt thanks go to my family for their unwavering support and encouragement throughout my academic endeavors, especially during the demanding process of research and thesis writing.

I cannot overlook the support from my girlfriend, Estefania, and her family. Their warm welcome during my times away from Portugal provided a comforting sense of home, which was indispensable. Estefania’s support, her celebration of my achievements, and her encouragement during challenging times have been a source of motivation and strength.

This accomplishment is a testament to the support and encouragement of everyone mentioned, for which I am profoundly grateful.

\begin{flushright}
    André Martins Rodrigues 
\end{flushright}

}
